{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-04-25 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@

    \section{Practical enhencements}
        In this section, we provide results for the faster convergence rate of examples listed from the previous section.

>>>>

            This example won't give specific rules for calculating $\tilde x_k$ for monotone descent. 
            Chambolle's restart has specific rules for choosing the stepsizes based on the estimates of the Lipschitz constants. 

@@

    \section{practical enhancement}
        In this section, we provide results for the faster convergence rate of examples listed from the previous section. 
    \section{restarting with gradient and function values}

\section{Primal Dual Lagrangian for LP}
